Stay in shape! Homework exam II

### 2016-03-24 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
special constraints idea...

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
Let $H_{int}$ be the intersection of halfplanes of $H$.
\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

		$H_{int}$ never crosses the x axis,
		so it exists entirely above or below $y=0$. Or the intersection is empty.

@@

		$H_{int}$ has no parallel line  to te x axis and
		at most one line crossing the x axis.

@@

		$H_{int}$ crosses the x-axis at least 2 times and
		if there is a line parallel to the x axis then both x-axis crossing
		to be in range of the diameter of the disk.

@@

		$H_{int}$ produces an area with lines parallel to the x-axis.

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
	\State 
	\State 
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
%TODO: een beeetje overtypen van 4.5
Let $1 \leq i \leq n$, and let $c_i$ be the

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pst-solides3d}
\usepackage{auto-pst-pdf}
\usepackage{tikz}
\usepackage{enumerate}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\begin{document}
\author{Jappie Klooster}
\title{Stay in shape! Homework exam II}
\maketitle
\section{A disk and some half-planes}
\subsection{Per case, what can you say about $H$}
We number the half-planes of $H$: $h_1, h_2,\dots,h_i$.
Let $H_{i}$ be the set of the first $i$ constraints with special constraints
$x_1$ and $x_2$ both one unit away from the x axis and pointing to the x
axis, and
let $C_{i}$ be the feasible region defined by these constranits:

\[ H_i := \{x_1, x_2, h_1, h_2,\dots, h_i\}\]
\[ C_i := x_1 \cap x_2 \cap h_1 \cap h_2 \cap \dots \cap h_i\]

\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

	The intersection $C_i$ is empty.

@@

		$C_i$ has no parallel line  to te x axis and
		at most one line crossing the x axis.

@@

		$C_i$ crosses the x-axis at least 2 times and
		if there is a line parallel to the x axis then both x-axis crossing
		to be in range of the diameter of the disk.

@@

		$C_i$ produces an area with lines parallel to the x-axis.

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
%TODO: een beeetje overtypen van 4.5
Let $1 \leq i \leq n$, let $C_i$ be the defined as above and let $d_i$ be
the largest disk in $C_i$. Then we have
\begin{enumerate}[i]
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
\end{enumerate}
